---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB statistics 

Here we inspect the types of structures in the main database for 3D biomolecular data - the PDB 

```{r}
# read in file
stats <- read.csv("Data Export Summary.csv",row.names=1)

# calculate precentage values for each "method"
stats
ans <- stats$Total/sum(stats$Total)*100 
names(ans) <- rownames(stats)
round(ans,2)
```


>Q1: determine the percentage of structures solved by X-Ray and Electron Microscopy. 

For X-ray: 88.950 %

For Electron microscopy: 2.72 %

>Q2: determine what proportion of structures are protein? Aim to have a rendered GitHub
document with working code that yields your answers.

```{r}
# Propertion of structures are proteins 
round(sum(stats$Proteins)/sum(stats$Total)*100,2)
```


>Q2: Type HIV in the PDB website search box on the home page and determine how many
HIV-1 protease structures are in the current PDB?



























